Revisited hidden weight bit function

### 2024-11-06 RevisedHiddenWeight.tex
More typos

\begin{definition}[Majority function]\label{def:maj}
    The \emph{majority function} in $n$ variables is the Boolean function $\textsf{Maj}\in\BN$ defined as:
    \[
        \textsf{Maj}(x)=0\iff\w(x)<n/2.
    \]
\end{definition}

@@

\begin{Prop}[Nonlinearity of some functions from $\WD{1}{n}$\label{prop:wwd1}]
Let $n\in \N^*$ even, the following hold for the following functions in $\WD{1}{n}$: 
\begin{itemize}
	\item (\eg ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\textsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
	\[
	\NL(\textsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
	\]
	\item (\cite{DAM:WCST14}, Theorem $3$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies:
	\[
	\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}.
	\]	
\end{itemize}
\end{Prop}

@@

		$f$  & $4$  & $22$  & $102$  &  $458$ & $1902$ & $7842$ & $31680$\\
\hline
	\end{tabular}
	\caption{Comparison of the nonlinearity.}
	\label{table:comparisonsNL}
\end{table}

>>>>

\begin{definition}[Majority function]\label{def:maj}
    The \emph{majority function} in $n$ variables is the Boolean function $\mathsf{Maj}\in\BN$ defined as:
    \[
        \mathsf{Maj}(x)=0\iff\w(x)<n/2.
    \]
\end{definition}

@@

\begin{Prop}[Nonlinearity of some functions from $\WD{1}{n}$\label{prop:wwd1}]
Let $n\in \N^*$ even, the following hold for the following functions in $\WD{1}{n}$: 
\begin{itemize}
	\item (\eg ~\cite{DCC:DalMaiSar06}, Theorem $3$) The majority function $\mathsf{Maj}_n$ introduced in Definition~\ref{def:maj} satisfies:
	\[
	\NL(\mathsf{Maj}_n)=2^{n-1}-\binom{n-1}{\frac n2}.
	\]
	\item (\cite{DAM:WCST14}, Theorem $3$) The HWBF $h$ introduced in Definition~\ref{def:hwbf} satisfies:
	\[
	\NL(h)=2^{n-1}-2\binom{n-2}{\frac{n-2}{2}}.
	\]	
\end{itemize}
\end{Prop}

@@

		$f$  & $4$  & $22$  & $102$  &  $458$ & $1902$ & $7842$ & $31680$\\
\hline
	\end{tabular}
	\tablecaption{Comparison of the nonlinearity.}
	\label{table:comparisonsNL}
\end{table}
